---
title: "Untitled"
author: "Daniel WU"
date: "3/4/2018"
output: html_document
---

```{r, echo=FALSE}
load("rcourse_lesson2_environment.RData")
```

# Introduction

I looked at how common my name, "Daniel", is in the United States population both by year and sex. 

# Results

## Prevalence by Year

Below is a plot for how the proportion of people with the name "Daniel" (log base 10 transformed) has changed over time. Overall the trend is pretty flat, with maybe a slight increase over time.

```{r, fig.align='center'}
year.plot
```
To test if there is a significant effect of year a linear model was built. Proportion of the population log base 10 transformed was the dependent variable and year the independent variable. As shown below, year was not significant, although the coefficients do show a positive slope.

```{r}
year.lm
```

## Prevalence by Year

Below is a plot for how the proportion of people with the name "Daniel" (log base 10 transformed) has changed over time. Overall the trend is pretty flat, with maybe a slight increase over time.

```{r, fig.align='center'}
sex.plot
```
To test if there is a significant effect of year a linear model was built. Proportion of the population log base 10 transformed was the dependent variable and year the independent variable. As shown below, sex was significant

```{r}
sex.lm
```

# Conclusion